The paper on \Large \bf Blockchain Frontrunning

### 2018-08-27 frontrunning/Latex/sections/paper.tex
[frontrunning] related work - fingerprint approach

\subsection{Recent Literature on Blockchain frontrunning}

>>>>

\subsection{Recent Literature on Blockchain front-running}

Aune~\etal\cite{aune2017footprints} discuss how the lack of time priority between broadcasting a transaction and its validation by miners on a blockchain based system would lead to the market information leakage. As mentioned in Section~\ref{sec:What is frontrunning?}, the information leakage results the entire system to be vulnerable to the front-running. They also propose a cryptographic approach to prevent any decentralized system from front-running. In this approach, which is similar to commit and reveal, a transaction hash (fingerprint) is broadcast to the network to secure time priority while not revealing the information. Once the hash is processed and assigned an index and timestamp, the transaction details are broadcast. This makes the transaction and its has to be executed at their reserved time priority and not vulnerable to the front-running.
